Supplementary Information

### 2015-06-18 manuscript/supplement.tex
updated supplement and fixed parentheses in coverletter

\subsection*{Appendix S2: Supplemental Figures}

>>>>

\subsection*{Appendix S2: Supplemental Methods and Results - scaling Relationships with S}

  \subsubsection*{Methods}

    The scaling relationships between link density ($Z$) and species richness ($S$)
    has been shown to be a power law~\citep{Riede2010} of the form

    \begin{equation}
    \label{Power}
    Z_{i} \sim \alpha S_{i}^{\beta}  ,
    \end{equation}

    \noindent which is often re-expressed in logarithmic form

    \begin{equation}
    \label{Loglog}
    \log{Z_{i}} \sim \log{\alpha} + \beta\log{S_{i}}  .
    \end{equation}

    \noindent Although these relationships are very similar, they imply different error distributions~\citep{Xiao2011}.
    Specifically, equation~(\ref{Power}) implies a normally-distributed, additive error and equation~(\ref{Loglog}) a lognormal,
    multiplicative error. As we have no \emph{a priori} reason to believe that our dataset has one error distribution
    over another, we follow the recommendations in~\citet{Xiao2011} and compared the two
    model formulations explicitly. The model with the error distribution most resembling that observed in the empirical
    data was then used to test for potential effects of latitude.

    Although scaling relationships between species richness and generality or
    species richness and vulnerability have not been explicitly examined (but see scaling 
    relationships for the standard devaitions of each property in~\citet{Riede2010}), we expect that they will follow
    power laws similar to that of the relationship between species richness and links per species.
    This is because the links taken into account in calculating generality and vulnerability are subsets 
    of the total links included when calculating links per species. As with links per species, we explicitly 
    compared the error distributions of models for generality and vulnerability using
    both the power-law and logarithmic formulations. 
    In each case, we used the best-fitting equation as a template when assessing the effect of latitude on scaling with
    species richness.

  \subsubsection*{Results}

    When considering the relationships between species richness or the proportions 
    of basal resources, intermediate consumers, or top predators and all response variables 
    (link density, generality, vulnerability), equation~(\ref{Loglog}) had a
    lower AIC than did equation~(\ref{Power}). This indicates that the
    data support an assumption of multiplicative lognormal error better than an
    assumption of additive normal error. That is, models where $\epsilon$ is
    modelled as an additive term on
    the logarithmic scale provide a better description of the data than models
    where $\epsilon$ is modelled as an additive term on the arithmetic scale.  
    We therefore used logarithmic-form models when assessing the
    effect of latitude on scaling relationships  with species richness.

\subsection*{Appendix S3: Supplemental Methods and Results - relationships with latitude}

  \subsubsection*{Methods}

    To determine whether there were latitudinal gradients in food-web structure,
    we first examined simple linear relationships between latitude and each of 
    species richness, links per species, generality, vulnerability, and proportions
    of basal resources, intermediate consumers, and top predators. We fit models of the form

    \begin{equation}
    \label{Latfull}
    S_{i} = \alpha_{0} + \alpha_{1} L_{i} + \alpha_{2} E_{i} + \alpha_{3} L_{i} E_{i} + \epsilon_{i} ,
    \end{equation}

    \noindent where $S_{i}$ is the species richness of web $i$, $L_{i}$ its absolute
    latitude (degrees north or south  regardless of direction), $E_{i}$ is a categorical
    variable indicating the ecosystem type of network $i$ (comprising terms for stream, 
    marine, lake, and terrestrial networks with estuarine
    networks providing the intercept) and $\epsilon_{i}$ a residual error term. 
    We next calculated the AIC
    of the maximal model as well as the AIC's of a suite of candidate simplified models identified
    using the R~\citep{R} function dredge from package MuMIn~\citep{MuMIn}. 
    Simplified models were obtained by
    systematically removing all possible combinations of terms from the full model.
    The best-fitting model was then determined to be the model with the fewest terms 
    where $\Delta$AIC\textless2. If several models shared the fewest number of terms 
    and had $\Delta$AIC\textless2, the model with the lowest AIC in that set was chosen as the best-fit
    model.

  \subsubsection*{Results}
    Contrary to the expected latitudinal gradient, the best-fit version of
    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
    relationship was robust to the removal of three outliers (based on Cook's Distance). 
    There were also relationships between latitude and link density and latitude and vulnerability
    in stream food webs, but these trends were non-signficant after the removal of three outliers.
    Link density and vulnerability did not vary with latitude in any other ecosystem type.
    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
    latitude in any ecosystem type.

    The relationships between latitude and the proportions of species at each trophic level were broadly similar
    to the relationship between latitude and species richness. 
    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
    but did not vary with latitude in estuarine, marine, lake, or terrestrial 
    food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
    The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
    The proportion of top predators did not vary with latitude in 
    estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
    webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
    All of these trends were robust to the removal of outliers.

\subsection*{Appendix S4: Supplemental Figures}

\begin{figure}[H]
\includegraphics[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts_observed.eps}
\caption{Scaling relationships for link density, generality (number of prey), 
and vulnerability (number of predators) against the proportions of basal resources (\% Basal),
intermediate consumers (\% Intermediate), top predators (\% Top), and species richness of a food web. 
For each relationship, we show observed values (grey circles) and the scaling relationship, neglecting 
any effects of habitat type or latitude (N=163 food webs). See Fig. 1 (\emph{Main Text}) to compare with 
observed values correcting for the effects of habitat type and latitude. }
\label{props_v_lat_obs}
\end{figure}
